Brief Announcement: A Family of Leaderless Generalized-Consensus Algorithms

### 2016-02-10 podc16/paper2.tex
started explaining the algo, and other comments.

@@

\todo{Why do we need $R$ if we already define what commute and non-commutative means?}

\todo{About the uniqueness of commands: why not leave that our of our scope?}

\todo{Why not base everything on C-Structs? We can say that two commands commute when $\sigma\bullet c_1\bullet c_2 =  \sigma\bullet c_2\bullet c_1 $ for every cstruct $\sigma$.}

@@

A dependency-set computation algorithm allows processes to announce a command $c$ and to learn about a suggested dependency set for a previously announced command.

@@

>>>>

\todo{Let's base everything on C-Structs; it will be easier. We can say that two commands commute when $\sigma\bullet c_1\bullet c_2 =  \sigma\bullet c_2\bullet c_1 $ for every cstruct $\sigma$.}

@@

@@

@@

\subsection{Implementing Leaderless Generalized Consensus}

Genearalized consensus~\cite{Lamport05GeneralizeConsensus} is a specification for state-machine replication algorithms. 
A generalized-consensus algorithm exposes the input actions $propose\left( c \right)$, for a command $c$, and $learn\left( \sigma \right)$, for a c-struct $\sigma$.
Moreover, a generalized-consensus algorithm must ensure that TODO.

We now propose an algorithm that uses the dependency-set computation abstraction and the map-agreement abstraction to implement generalized consensus. We therefore obtain a family of generalized consensus algorithms where each member of the family is obtained by using concrete dependency-set and map-agreement algorithms.

\todo{Explain the algorithm with pseudocode?}

\todo{Explain the graph processing algo independently? Its key property is that when $G1 \subseteq G2$ then $lin\left( c_1,G1 \right)$ is a prefix of $lin\left( c_2,G2 \right)$ or vice-versa.}
